EEOB563 -- Assignment #5

### 2019-03-13 assignments/5/Assignment_5.Rmd
Finished 5.5

## 5
I had problems with slurm so I couldn't start it until Tuesday evening, so it's still running. I will resubmit this assignment tomorrow with part 5 when it is done. I am expecting a runtime of $\ge$ 10 hours from what the others have told me, I don't remember the runtimes from the lab anymore.
This is my slurm script:

@@

>>>>

## 5
I had expected a runtime of $\ge$ 10 hours from what the others have told me, I don't remember the runtimes from the lab anymore. In reality, it only took about 6:30 hours though, so I was lucky.
This is my slurm script:

@@

Here is the tree, finally the tree is further away from the animals:

![ML tree with bootstrap support values](5/BootstrapSupport.png)
